---
title: "DAT 500 S "
author: "DuraiSundaramoorthi"
output: pdf_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## 2.3.1 Basic Commands
## Basic Commands Chunk 1

```{r}
x = c(1, 3, 2, 5)
x

x = c(1, 6, 2)
x

y = c(1, 4, 3)
y

length(x)

length(y)

x+y

ls()

rm(x,y)

rm(list = ls())

ls()
```


## Basic Commands Chunk 2

```{r}

?matrix

x = matrix(data = c(1,2,3,4), nrow = 2, ncol = 2)
x

x = matrix(c(1,2,3,4),2,2)
x

x = matrix(c(1,2,3,4),2,2,byrow = TRUE)
x

sqrt(x)
```


## Basic Commands Chunk 3

```{r}

set.seed(1)

x = rnorm(50)

x

mean(x)

sd(x)
```


## Basic Commands Chunk 4

```{r}
y = x + rnorm(50, mean=50,sd=0.1)
y

cor(x,y)

```

## Basic Commands Chunk 5

```{r}

set.seed(3)

y = rnorm(100)
mean(y)

var(y)

sqrt(var(y))

sd(y)

```

## 2.3.2 Graphics
## Graphics Chunk 6

```{r}
x = rnorm(100)
y = rnorm(100)

plot(x,y)

plot(x,y,xlab = "label for x-axis", ylab = "label for y-axis", main = "Plot of x vs y")

plot(x,y,col = "green")

```

## 2.3.5 Additional Graphical and Numerical Summaries
## Graphics Chunk 7
```{r}
library(ISLR)

# plot(cylinders, mpg)

plot(Auto$cylinders, Auto$mpg)
```

## Graphics Chunk 8
```{r}
attach(Auto)

plot(cylinders,mpg)

```

## Graphics Chunk 9
```{r}
cylinders = as.factor(cylinders)

plot(cylinders,mpg)
```


## Graphics Chunk 10
```{r}

plot(cylinders,mpg, col = "red")

plot(cylinders,mpg, col = "red", varwidth = T)

plot(cylinders,mpg, col = "red", varwidth = T, horizontal = T)

plot(cylinders,mpg, col = "red", varwidth = T, xlab = "Cylinders", ylab = "MPG")
```

## Graphics Chunk 11
```{r}

hist(mpg)

hist(mpg,col = 2)

hist(mpg,col = "red", breaks = 15)
```

## Graphics Chunk 12
```{r}

pairs(Auto)

pairs(~mpg + displacement + horsepower + weight + acceleration, Auto)

```

## Graphics Chunk 13
```

plot(horsepower,mpg)

identify(horsepower,mpg,name)
```

## Graphics Chunk 14
```{r}

summary(Auto)

summary(mpg)
```

## 2.3.3 Indexing Data
## Indexing Chunk 15

```{r}

A = matrix(1:16,4,4)
A

A[2,3]

A[c(1,3),c(2,4)]

A[1:3,2:4]

A[1:2,]

A[,1:2]

A[1,]

A[-c(1,3),]

dim(A)

```

## 2.3.4 Loading Data
## Loading Data Chunk 16

```

Auto = read.table("C:/C/DAT500S/Data/Auto.data")
fix(Auto)

Auto = read.table("C:/C/DAT500S/Data/Auto.data",header = T, na.strings = "?")
fix(Auto)

Auto = read.csv("C:/C/DAT500S/Data/Auto.csv",header = T, na.strings = "?")
fix(Auto)

```


## Loading Data Chunk 17

```{r}
dim(Auto)

Auto[1:4,]

Auto = na.omit(Auto)
dim(Auto)

names(Auto)
```

